Future challenges for Research Software Engineering

### 2025-09-24 future_challenges_for_RSEng.tex
replace word
drop paragraph as it is already a few lines above

\subsection{Ethics and Social Considerations}
\begin{whatis}{}{ethics}
The principles of Good Scientific Practice~\cite{dfg_gsp} have been a cornerstone in the conduct of research.
But their relevance hinges on constant updates in light of how research is performed.
By 2035, accepted rules on the use of AI in research tasks and software development have been achieved.
Open Science and Open Research are by then well-established in academia, and supported by respective open research software
strategies of the political actors.
A strong culture of data awareness and protection has been sustained and is actively maintained across the research community.
\end{whatis}

@@

A code of ethics and professional conduct for RSEs should be developed by institutions together with RSEs themselves.
This can then form the basis for institutional policies and guidelines as well as serve as a background for individual developers to consider how software can be used.

>>>>

\subsection{Ethics and Social Considerations}
\begin{whatis}{}{ethics}
The principles of Good Scientific Practice~\cite{dfg_gsp} have been a cornerstone in the conduct of research.
However, their relevance hinges on constant updates in light of how research is performed.
By 2035, accepted rules on the use of AI in research tasks and software development have been achieved.
Open Science and Open Research are by then well-established in academia, and supported by respective open research software
strategies of the political actors.
A strong culture of data awareness and protection has been sustained and is actively maintained across the research community.
\end{whatis}

@@
